HBCC - sgACC - FEATURECOUNTS - GRCh38 - CQN

### 2020-05-20 individual-cohorts/HBCC_sgACC_FEATURECOUNTS_GRCh38_CQN.Rmd
most updated config

knit2synapse::createAndKnitToFolderEntity(file = "HBCC_sgACC_FEATURECOUNTS_GRCh38_CQN.Rmd",
                                          parentId ="syn22012942",
                                          folderName = 'HBCC - sgACC - DREAM - FEATURECOUNTS - GRCh38 - CQN')
```

@@

# Github link
thisRepo <- getRepo(repository = "CommonMindConsortium/covarr-de", ref="branch", refName='master')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=thisFileName)
```
### Data download
#### Obtain effective count matrix and metadata from synapse.
```{r download.data, cache=TRUE}
downloadFile <- function(id){
  fread(synGet(id)$path, data.table = F)
}
downloadFile_version <- function(id , version){
  fread(synGet(id, version = version)$path, data.table = F)
}

>>>>

knit2synapse::createAndKnitToFolderEntity(file = "individual-cohorts/HBCC_sgACC_FEATURECOUNTS_GRCh38_CQN.Rmd",
                                          parentId ="syn22012942",
                                          folderName = 'HBCC - sgACC - DREAM - FEATURECOUNTS - GRCh38 - CQN')
```

@@

# Github link
thisRepo <- getRepo(repository = "CommonMindConsortium/covarr-de", ref="branch", refName='master')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('individual-cohorts/',thisFileName))
```
### Data download
#### Obtain effective count matrix and metadata from synapse.
```{r download.data, cache=TRUE}
downloadFile <- function(id){
  fread(synGet(id)$path, data.table = F)
}
downloadFile_version <- function(id , version){
  fread(synGet(id, version = version)$path, data.table = F)
}
